A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-07 MSR-Scratch.tex
Dataset Construction

\title{A dataset of Scratch programs,\\Scraped, Shaped and Graded}

@@

The goal of this paper is to present an open and timely dataset of recent Scratch programs, along with their metadata, that can facilitate quantitative research in the fields of source code analysis and computing education.
The dataset contains 250 thousand Scratch projects, from 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnote{{add anonymized address}} which includes, for each Scratch project, its metadata and the program data, along with project grading results from the Dr. Scratch quality assessment tool \cite{moreno_automatic_2014}.

\section{Dataset Construction}
a description of the methodology used to gather it (preferably with the tool used to create/generate the data)

>>>>

\title{A dataset of Scratch programs,\\Scraped, Shaped and Scored}

@@

The goal of this paper is to present an open and timely dataset of recent Scratch programs, along with their metadata, that can facilitate quantitative research in the fields of source code analysis and computing education.
The dataset contains 250 thousand Scratch projects, from 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnote{{add anonymized address}} which includes, for each Scratch project, its metadata and the program data, along with programming mastery scoring results from the Dr. Scratch quality assessment tool \cite{moreno_automatic_2014}.

\section{Dataset Construction}
\label{dataset}

\subsection{Data collection}
To collect the data from the web interface of the Scratch project repository we built a scraping program.
The web scraping program, called Kragle, starts by reading the Scratch projects page\footnote{\label{scratchpublic}\url{https://scratch.mit.edu/explore/projects/all/}} and thus obtains the project identifiers of projects that were most recently shared.
Subsequently, Kragle retrieves the JSON code for each of the listed projects\footnote{For a given project id $x$, the program's JSON representation can be obtained via \url{https://cdn.projects.scratch.mit.edu/internalapi/project/x/get}}.

We ran Kragle on March 2nd 2016 for 24 hours and, during that time, it obtained the JSON code for \nPrograms projects. Out of those, we failed to parse and further analyze 2,367 projects due to technical difficulties with the JSON files.
Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/TUDelftScratchLab/ScratchDataset}}

Once we obtained the Scratch projects, we parsed the JSON files according to the specification of the format\footnote{\url{http://wiki.scratch.mit.edu/wiki/Scratch_File_Format_(2.0)}}.
This resulted in a list of used blocks per project, within the sprites and the stage of the project.
We also cross referenced all blocks with the Scratch wiki to determine the shapes and the category of all blocks.
For example, \texttt{When Green Flag Clicked} is a \emph{Hat block} from the \emph{Events category}.

\subsection{Calculation of programming mastery scores}
\fenia{Description of how the mastery metrics for       
	[Abstraction]
	,[Parallelism]
	,[Logic]
	,[Synchronization]
	,[FlowControl]
	,[UserInteractivity]
	,[DataRepresentation]
	,[Mastery]
	,[Clones]
	,[CustomBlocks]
	,[InstancesSprites]
	were calculated}

\subsection{Importing the data}
\label{dataAnalysis}
All scraped project data and metadata, including the list of used blocks and parameters, were imported in a relational database.
We also imported the data on the shapes and the categories of the Scratch blocks.
We then used SQL queries for normalizing the data and bringing it in its final schema, which is drawn in Figure???
